There once was a grid at ol' Carkeek

### 2016-04-12 Manuscript/v0.0/carkeek_grid.tex
finalize outlier removal

We assessed PCR contamination by evaluating the dissimilarity of replicate PCRs of the same DNA sample, and removed one sample for which the Bray-Curtis dissimilarities between itseld and the other replicates exceeded 0.1 (lib_B_tag_GCGCTC).

@@

>>>>

We assessed PCR contamination by evaluating the dissimilarity of replicate PCRs of the same DNA sample, and removed one sample for which the Bray-Curtis dissimilarities between itseld and the other replicates exceeded 0.1 (lib\_B\_tag\_GCGCTC).

@@

We assessed the consistency of PCR by conducting 4 replicate PCRs for each environmental sample and calculating the mean pairwise Bray-Curtis dissimilarity of the resulting communities (scaled to minimum read depth per sample). 
92 of the 96 amplicon samples had mean Bray-Curtis dissimilarity $\leq$ 0.052; 1 sample had a value of 0.341, which elevates the value of the other replicates. 
After removal of this sample, the highest mean Bray-Curtis dissimilarity among replicates within an environmental sample was 0.034.
